% b_entries.tex - Terms beginning with B
\chapter*{B}
\addcontentsline{toc}{chapter}{B}

\dictentry{B2B Payments (Business-to-Business)}{/bi틣 tu틣 bi틣 틛pe톩m톛nts/, \textit{n.}}{
Transactions between two or more businesses, such as payments made by a
manufacturer to a wholesaler, facilitated by a wide range of commercial
payment solutions.
}
\indexentry{B2B Payments (Business-to-Business)}

\dictentry{Back-End Processor}{/b칝k 톝nd 틛pr톔틣s톝s톛r/, \textit{n.}}{
A data company contracted by an acquirer to provide processing services,
including routing payments from the issuing bank to the merchant to
complete transactions.
}
\indexentry{Back-End Processor}

\dictentry{Bank Identification Number (BIN)}{/b칝콂k a톩틟d톝nt톩f톩틛ke톩툮톛n 틛n툷mb톛r/, \textit{n.}}{
The first four to six digits on a payment card that identify the bank or
financial institution that issued the card, as well as its location and
type.
}
\indexentry{Bank Identification Number (BIN)}

\dictentry{Bank Routing Number}{/b칝콂k 틛ru틣t톩콂 틛n툷mb톛r/, \textit{n.}}{
The nine-digit number appearing at the bottom of a check that identifies
the financial institution responsible for the account.
}
\indexentry{Bank Routing Number}

\dictentry{Basis Point}{/틛be톩s톩s p톖톩nt/, \textit{n.}}{
A very small unit used to describe rate changes. One basis point equals
0.01\% (one-hundredth of a percent), and 100 basis points equals 1\%.

\example{If an interchange rate increases from 1.50\% to 1.75\%, that is a
25-basis-point increase.}
}
\indexentry{Basis Point}

\dictentry{Batch}{/b칝t툮/, \textit{n.}}{
A group of captured transactions awaiting settlement, typically processed
multiple times throughout the day.
}
\indexentry{Batch}

\dictentry{Batch Processing}{/b칝t툮 틛pr톔틣s톝s톩콂/, \textit{n.}}{
The grouping and processing of related transactions at the same time,
usually by the same computer application, to improve efficiency.
}
\indexentry{Batch Processing}

\dictentry{Big Data}{/b톩토 틛de톩t톛/, \textit{n.}}{
Large and complex data sets analyzed to identify patterns of behavior,
often used to develop business strategies.
}
\indexentry{Big Data}

\dictentry{Bitcoin}{/틛b톩tk톖톩n/, \textit{n.}}{
A decentralized digital currency that is not backed by any central bank
or government, used for transactions with vendors accepting it as payment.
}
\indexentry{Bitcoin}

\dictentry{Blockchain}{/틛bl톔틣kt툮e톩n/, \textit{n.}}{
A digital ledger that records cryptocurrency transactions in chronological
order, ensuring transparency and security without central bookkeeping.
}
\indexentry{Blockchain}

\dictentry{Breach}{/bri틣t툮/, \textit{n.}}{
An incident in which security measures are compromised, leading to
unauthorized access to sensitive cardholder data.
}
\indexentry{Breach}

\dictentry{Business Day}{/틛b톩zn톛s de톩/, \textit{n.}}{
A standard day for conducting business, excluding weekends and holidays,
during which most retail locations and financial institutions are open.
}
\indexentry{Business Day}
