% d_entries.tex - Terms beginning with D
\chapter*{D}
\addcontentsline{toc}{chapter}{D}

\dictentry{DUKPT}{/ˈdʌk-pɪt/, \textit{abbr.}}{
Derived Unique Key Per Transaction. A cryptographic key management scheme used
in electronic payments to ensure that a unique, one-time encryption key is
generated for every single transaction. DUKPT prevents "master key"
compromise; even if an attacker steals the key for a specific transaction, they
cannot use it to decrypt any past or future transactions from the same device.

\example{When you enter your PIN at a checkout terminal, the device uses DUKPT to
encrypt the PIN with a key that will never be used again. Even if a hacker
intercepted that specific message, they couldn't use that information to steal
PINs from future customers.}

\analogy{Biological}{Like an \textbf{Enzyme Blueprint}. Imagine a master DNA
code (the Base Derivation Key) kept safe in a cell's nucleus. Each individual
cell (POS terminal) is given a unique genetic seed derived from that DNA. To
perform a task (a transaction), the cell produces a specific, one-time enzyme
(the session key). Once the task is done, the enzyme is immediately broken down
and disappears. Knowing the structure of one used enzyme doesn't allow you to
predict the next one, nor can you use it to reconstruct the master DNA.}

\crossref{\textbf{Encryption}, \textbf{HSM}, \textbf{Key Management}, \textbf{PIN}}

\etymology{Developed in the late 1980s and formalized in the ANSI X9.24
standard. It became the industry standard for protecting PINs at the point of
sale.}
}
\indexentry{DUKPT}

% Additional D terms will be added here
